Quick, Draw! Image Classification

### 2018-12-07 report/draft.tex
section 2.1 looks good to me

TODO: explain how we used a CNN or anything else not covered in class

@@

>>>>

Convolutional networks, also known as convolutional neural networks(CNNs),
are a specialized kind of neural network for processing data that has a
known grid-like topology. Convolutional networks have been tremendously
successful in practical applications. The name “convolutional neural network”
indicates that the network employs a mathematical operation called
convolution. Convolution is a specialized kind of linear operation.
Convolutional networks are simply neural networks that use convolution
in place of general matrix multiplication in at least one of their layers. See
Figure \ref{fig:CNN} in the Appendix for a visual representation of a CNN.

CNN architectures are usually composed of the building blocks as described
below:

\begin{enumerate}
\item \textbf{Convolution:} Convolution operation helps to extract features
  from the input image. The ﬁrst argument to the convolution is often referred
  to as the input , the second argument as the feature detector (kernel) and
  the output as the feature map. The convolution operation takes the dot
  product of feature map and the input to detect features. Since each
  convolution operation only focuses on a part of an image enabling parameter
  sharing which helps to reduce the number of free parameters compared to a
  fully connected neural network, allowing the network to be deeper with
  fewer parameters.

  \begin{itemize}
  \item \textbf{Strides:} Stride is the number of pixels jumps between
    each convolution operation performed on the input matrix. When the stride
    is 1 then we move the filters to 1 pixel at a time. Increasing the stride
    parameter reduces the output volume of the convolution since the jumps
    are larger.
  \item \textbf{Padding:}Padding helps to detect features present at the
    border by adding a dummy values around the edge. Since convolution
    operations collect most information from the center of the image, adding
    padding allows the border pixels to be weighed more during the convolution
    operation.
  \end{itemize}

  See Figure \ref{fig:CNNStridePad} in the Appendix for an example of Stride
  and Padding.

\item \textbf{Pooling Layer:} Pooling layers section helps to reduce the
  number of parameters when the images are too large. Spatial pooling
  (subsampling or downsampling) reduces the dimensionality of each map,
  retaining important information. These can be of different types:
  (1) Max Pooling - takes the largest element (most important feature)
  from the rectified feature map (2) Average Pooling - averages all the
  pixel values (3) Sum Pooling. sum of all pixels values. See figure
  \ref{fig:CNNPooling} for a visualization of a Pooling Layer.

\item \textbf{Fully Connected Layer:} The layer we call as FC layer, we
  flattened our matrix into vector and feed it into a fully connected layer
  like neural network.
  \end{enumerate}

@@

\section{Appendix}

\begin{figure}[h!]
  \begin{center}
    \includegraphics[scale=0.5]{fig5}
    \end{center}
  \caption{CNN Architecture Example}
  \label{fig:CNN}
\end{figure}

\begin{figure}[h!]
  \begin{center}
    \includegraphics[scale=0.5]{fig6}
    \end{center}
  \caption{Convolution operation with stride=1, padding=None}
  \label{fig:CNNStridePad}
\end{figure}

\begin{figure}[h!]
  \begin{center}
    \includegraphics[scale=0.5]{fig7}
  \end{center}
  \caption{Example of Max Pooling}
  \label{fig:CNNPooling}
  \end{figure}
